Cross-relaxation in dense ensembles of NV centers and application to magnetometry

### 2022-12-03 Talks/Soutenance 2022/presentation.tex
tata

\begin{frame}{Depolarization of dense NV ensemble at low magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{slide_presentation_sujet}
\end{frame}

\begin{frame}{LFDM experimental setup}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_principle_LFDM}
\end{frame}

@@

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry on irregular surfaces}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field}
\end{frame}

@@

>>>>

\begin{frame}{Depolarization of dense NV ensemble at low magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{slide_low_field_depolarization_f_-3}
\end{frame}

\begin{frame}{Depolarization of dense NV ensemble at low magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{slide_low_field_depolarization_f_-2}
\end{frame}

\begin{frame}{Depolarization of dense NV ensemble at low magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{slide_low_field_depolarization_f_-1}
\end{frame}

\begin{frame}{Depolarization of dense NV ensemble at low magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{slide_low_field_depolarization_f}
\end{frame}

\begin{frame}{LFDM experimental setup}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_principle_LFDM_f-2}
\end{frame}

\begin{frame}{LFDM experimental setup}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_principle_LFDM_f-1}
\end{frame}

\begin{frame}{LFDM experimental setup}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_principle_LFDM_f}
\end{frame}

@@

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f-6}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f-5}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f-4}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f-3}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f-2}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f-1}
\end{frame}

\begin{frame}{Comparison with the state of the art}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_comparison_litterature_f}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-3}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-2}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-1}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f}
\end{frame}

@@

\begin{frame}{LFDM: shot-noise limit}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_bonus_shot_noise_limit}
\end{frame}
